Growth of _E. coli_ in mSSB lab 

### 2022-10-17 mssb_2.2_2022.Rmd
uploading mssb files
adding github formatted versions

---
title: "Growth of _E. coli_ in mSSB lab "
author: "Charlotte Henson and Shahaf Cohen"
date: "October 2022"
output:
  html_document:
    code_folding: hide
---

@@

@@

Finally we explore the limits of detection given our experimental setup.
```{r limits of detection, echo=TRUE}
# To explore the limits of detection we will test fluorescence of plasmid #2 
# (261) detected at 590nm (two plots for two excitation wavelengths).

>>>>

---
title: "Growth of _E. coli_ in mSSB lab "
author: "Charlotte Henson and Shahaf Cohen"
date: "October 2022"
output:
  html_document:
    code_folding: hide
    keep_md: true
---

@@

This comparison is done with the R standard t-test, pairwise. Among the many combinations we found one with a p=0.03, which we plotted below.

@@

Finally we explore the limits of detection given our experimental setup. We plot the detection of plasmid 261 without any integrase in the "mKate" channel (fluorescence intensity at 590 nm). We also plot the untransformed WT _E. coli_. We see the readings are non-zero in the channel, even when reading samples that should not be emitting fluorescence. 
```{r limits of detection, echo=TRUE}
# To explore the limits of detection we will test fluorescence of plasmid #2 
# (261) detected at 590nm (two plots for two excitation wavelengths).
